Preventing Runtime Errors of Redis at Compile Time

### 2015-11-20 paper.tex
Categories and Subject Descriptors & Keywords

\paragraph{Categories and Subject Descriptors}
\paragraph{Keywords}
Haskell; type-level programming; database query language; Redis;
\end{abstract}

@@

The function \mintinline{haskell}{sadd} takes a key and a list of values as
 arguments, and returns an \mintinline{haskell}{Integer} on success, or
 returns a \mintinline{haskell}{Reply}, a low-level representation of replies
 from the Redis server, in case of failues. All wrapped in
 \mintinline{haskell}{Redis}\footnotemark, the context of command execution.

@@

\emph{Indexed monads} (or \emph{monadish},
 \emph{parameterised monad})\cite{indexedmonad}
 can be used\cite{typefun}\cite{staticresources} to model such preconditions and
 postconditions in types. An indexed monad is a type constructor that takes
 three arguments: an initial state, a final state, and the type of a value that
 an action computes, which can be read like a Hoare triple\cite{kleisli}.

@@

Type families have a wide variety of applications. They can appear inside type
 classes\cite{tfclass}\cite{tfsynonym}, or at toplevel. Toplevel type families
 can be used to compute over types, they come in two forms: open\cite{tfopen}
 and closed \cite{tfclosed}.

@@

Since Haskell has a \emph{phase distinction}\cite{phasedistinction}, types are
 erased before runtime. It's impossible to obtain information directly from
 types, we can only do this indirectly, with
 \emph{singleton types}\cite{singletons}.

@@

Redis also provides \emph{transactions}, another context for executing commands.
Redis trasanctions are atomic in the sense that, all commands in a transaction
 will executed sequentially, and no other requests issued by other clients will
 be served \textbf{in the middle}.\footnotemark In contrast, we cannot make such
 a guarantee in the ordinary context, which may destroy the assertions we made
 in types.

@@

While Redis can be viewed as a non-relational database system (although Redis
 seems reluctant to admit this in recent years), there also similar goals on
 relational database systems, trying to achieve a safer database interface by
 making them statically checked.
 \emph{HaskellDB}\cite{haskelldb}\cite{haskelldbimproved} expresses quries
 with relational algebra-like combinators, wrapped in phantom types. Or as
 examples, at first to demonstrate the power of dependent types in
 Agda\cite{pi}, and then with singletons in Haskell\cite{singletons}.

>>>>

\category{D.3.3}{Programming Languages}{Language Constructs and Features}
\category{F.3.1}{Specifying and Verifying and Reasoning about Programs}{Specification techniques}
\category{H.2.3}{Database Management}{Languages}
\keywords{Haskell; type families; type-level literals; indexed monad; Redis; database query language}
\end{abstract}

@@

The function \mintinline{haskell}{sadd} takes a key and a list of values as
 arguments, and returns an \mintinline{haskell}{Integer} on success, or
 returns a \mintinline{haskell}{Reply}, a low-level representation of replies
 from the Redis server, in case of failures. All wrapped in
 \mintinline{haskell}{Redis}\footnotemark, the context of command execution.

@@

\emph{Indexed monads} (or \emph{monadish},
 \emph{parameterised monad})\cite{indexedmonad}
 can be used\cite{typefun, staticresources} to model such preconditions and
 postconditions in types. An indexed monad is a type constructor that takes
 three arguments: an initial state, a final state, and the type of a value that
 an action computes, which can be read like a Hoare triple\cite{kleisli}.

@@

Type families have a wide variety of applications. They can appear inside type
 classes\cite{tfclass, tfsynonym}, or at toplevel. Toplevel type families
 can be used to compute over types, they come in two forms: open\cite{tfopen}
 and closed \cite{tfclosed}.

@@

Since Haskell has a \emph{phase distinction, phasedistinction}, types are
 erased before runtime. It's impossible to obtain information directly from
 types, we can only do this indirectly, with
 \emph{singleton types, singletons}.

@@

Redis also provides \emph{transactions}, another context for executing commands.
Redis transactions are atomic in the sense that, all commands in a transaction
 will executed sequentially, and no other requests issued by other clients will
 be served \textbf{in the middle}.\footnotemark In contrast, we cannot make such
 a guarantee in the ordinary context, which may destroy the assertions we made
 in types.

@@

While Redis can be viewed as a non-relational database system (although Redis
 seems reluctant to admit this in recent years), there also similar goals on
 relational database systems, trying to achieve a safer database interface by
 making them statically checked.
 \emph{HaskellDB}\cite{haskelldb, haskelldbimproved} expresses quires
 with relational algebra-like combinators, wrapped in phantom types. Or as
 examples, at first to demonstrate the power of dependent types in
 Agda\cite{pi}, and then with singletons in Haskell\cite{singletons}.
